Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-12-17 code/analysis.Rmd
heteroskedasticity numero dos

r2mod <- list()
r2val <- list()
ktval <- list()
resids <- list()

for (k in 1:length(unique(pumpfinal$date))) {
  tempdata <- pumpfinal %>%
    filter(date == unique(pumpfinal$date)[k])

  r2mod[[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
  r2val[[k]] <- summary(r2mod[[k]])$r.squared
  ktval[[k]] <- -coef(r2mod[[k]])[2]
  resids[[k]] <- cbind(tempdata,resid = resid(r2mod[[k]]))

@@

>>>>

r2mod <- list()
r2val <- list()
ktval <- list()
resids_lin <- list()
nlsmod <- list()
resids_exp <- list()

for (k in 1:length(unique(pumpfinal$date))) {
  tempdata <- filter(pumpfinal) %>%
    filter(date == unique(pumpfinal$date)[k])

  r2mod[[k]] <- lm(data = tempdata, formula = log(mvc) ~ t)
  r2val[[k]] <- summary(r2mod[[k]])$r.squared
  ktval[[k]] <- -coef(r2mod[[k]])[2]
  resids_lin[[k]] <- cbind(tempdata,resid = resid(r2mod[[k]]))
  nlsmod[[k]] <- nls(data = tempdata, formula = mvc ~ a*exp(b*t), start = list(a = 80, b = 1e-4))
  resids_exp[[k]] <- cbind(tempdata, resid = resid(nlsmod[[k]]))

@@

resids_lin <- bind_rows(resids_lin) 
resids_exp <- bind_rows(resids_exp)

residplot <- function(dataset, title) {

  ggplot(aes(x = t, y = resid), data = dataset) +
    geom_point() +
    theme_bw() +
    theme(plot.title = element_text(hjust = .5)) +
    geom_hline(yintercept = 0, color = "black") +
    geom_smooth(color = "red") +
    labs(x = "Time (s)", y = "Residual Value") +
    ggtitle(title)

varplot <- function(dataset) {

dataset %>%
  group_by(t) %>%
  summarise(var = sd(resid)^2) %>%
  ggplot(aes(x = t, y = var)) +
  geom_line() +
  theme_bw() +
  labs(x = "Time (s)", y = "Residual Variance")

p1 <- residplot(resids_exp, title = "Exponental Model")
p2 <- residplot(resids_lin, title = "Linear Model")
p3 <- varplot(resids_exp)
p4 <- varplot(resids_lin)

heterosked_plot <- plot_grid(p1, p2, p3, p4, align = "h", labels = c("(a)","(b)","(c)","(d)"), scale = .9)

ggsave("../pics/heterosked.png", heterosked_plot, dpi = 600, height = 5)
